\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.6in}
\addtolength{\textheight}{1.2in}

\titleformat{\section}{\large\bfseries\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{8pt}{4pt}

\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeEntry}[4]{
  \item
  \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small#4} \\
  \end{tabular*}\vspace{-4pt}
}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in, itemsep=1pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{2pt}}
\newcommand{\resumeEntryListStart}{\begin{itemize}[leftmargin=0.0in, label={}, itemsep=2pt]}
\newcommand{\resumeEntryListEnd}{\end{itemize}}

\begin{document}

%----------HEADER----------
\begin{center}
    {\Huge \scshape Avery Morgan} \\ \vspace{2pt}
    Houston, TX $|$ 713-555-0148 $|$
    \href{mailto:avery.morgan.ai@example.com}{avery.morgan.ai@example.com} $|$
    \href{https://github.com/avery-morgan-ai}{github.com/avery-morgan-ai}
\end{center}

%----------SUMMARY----------
\section{Professional Summary}
% AGENT-EDIT-TARGET: summary
AI/ML engineer and Ph.D. researcher with 4+ years building production ML, generative-AI, and biomedical-vision systems. Delivered a 1.7M-record visual-QC workflow, 95\% resume-parser accuracy, 80\% job-matching success, and approximately 95\% accuracy/F1 for real-time fall detection.

%----------EDUCATION----------
\section{Education}
\resumeEntryListStart
  \resumeEntry{Gulfview Technical University}{Houston, TX}
    {Ph.D. Student, Electrical and Computer Engineering}{2025 -- Present}
  \resumeEntry{Pacifica Institute of Science}{Houston, TX}
    {M.S. Data Science (3.64/4.0) $|$ B.S. Math \& Computer Science (3.44/4.0)}{2021--2023 $|$ 2017--2021}
\resumeEntryListEnd

%----------EXPERIENCE----------
\section{Experience}
\resumeEntryListStart

  \resumeEntry{Graduate Research Assistant}{Jul. 2025 -- Present}
    {Gulfview Technical University}{Houston, TX}
  \resumeItemListStart
    % AGENT-EDIT-TARGET: experience-bullet-1
    \resumeItem{Built a visual-QC workflow over 1.7M segmentation/tracking predictions; achieved 90.5\% test accuracy and 0.764 F1 using out-of-fold evaluation and targeted error analysis.}
  \resumeItemListEnd

  \resumeEntry{Senior AI Engineer}{Dec. 2024 -- Jun. 2025}
    {Nimbus AI Products}{Houston, TX}
  \resumeItemListStart
    % AGENT-EDIT-TARGET: experience-bullet-2
    \resumeItem{Delivered an AI CRM and no-code LLM chatbot builder using predictive analytics, RAG, FastAPI, WebSocket, Docker, Kubernetes, and AWS SageMaker.}
  \resumeItemListEnd

  \resumeEntry{AI \& Data Engineer}{Apr. 2023 -- Nov. 2024}
    {Meridian Biomedical AI Lab}{Houston, TX}
  \resumeItemListStart
    \resumeItem{Built cardiovascular-imaging and real-time fall-detection models; reached approximately 95\% accuracy/F1, optimized embedded inference, and coauthored 2 peer-reviewed publications.}
  \resumeItemListEnd

  \resumeEntry{AI \& Data Engineer}{Aug. 2021 -- Apr. 2023}
    {TalentBridge Technologies}{Houston, TX}
  \resumeItemListStart
    \resumeItem{Built production resume parsing, candidate-job ranking, and policy-chatbot services, reaching 95\% parser accuracy and 80\% matching success.}
  \resumeItemListEnd

\resumeEntryListEnd

%----------PROJECTS----------
% The agent may SWAP any project below with a more relevant one from the
% portfolio file. Swapped-in projects must be formatted exactly like these.
\section{Projects}
\resumeEntryListStart

  % AGENT-SWAP-TARGET: project-1 | PORTFOLIO-ID: P05
  \resumeEntry{Cardiovascular Flow and Stenosis Analysis}{2023 -- 2024}
    {PyTorch, R2U Attention, Vision Transformer, OpenCV, DICOM}{Medical Computer Vision}
  \resumeItemListStart
    \resumeItem{Combined vessel isolation, catheter exclusion, retrograde-flow detection, stenosis localization, flow-time estimation, and vessel-kink analysis.}
  \resumeItemListEnd

  % AGENT-SWAP-TARGET: project-2 | PORTFOLIO-ID: P03
  \resumeEntry{No-Code LLM Chatbot Builder}{2025}
    {DeepInfra/OpenAI, RAG, AutoGen, crawl4ai, FastAPI, WebSocket}{Generative AI}
  \resumeItemListStart
    \resumeItem{Converted website content into retrieval-ready knowledge and exposed context-aware assistants through reusable APIs and real-time channels.}
  \resumeItemListEnd

\resumeEntryListEnd

%----------SKILLS----------
\section{Skills}
% AGENT-EDIT-TARGET: skills
\begin{itemize}[leftmargin=0.2in, itemsep=1pt]
  \small\item{\textbf{AI/ML:} Python, PyTorch, TensorFlow, Scikit-learn, OpenCV, Vision Transformers, EfficientNet, RAG, NLP, PaddleOCR}
  \small\item{\textbf{Production:} FastAPI, REST, WebSocket, Docker, Kubernetes, Airflow, MLflow, Git, AWS SageMaker, Google Cloud}
  \small\item{\textbf{Data \& Languages:} SQL, PostgreSQL, MySQL, MongoDB, Elasticsearch, Neo4j, Pinecone, Supabase, Rust, Java}
\end{itemize}

\end{document}
